Fast algebraic filtering of surfaces from 3D medical images with Julia

### 2019-06-12 src/implementation.tex
crumbs

\item extraction of the block views, depending on 3 Cartesian indices, from image arrays;

\item transform  each job \emph{from global} $[\ell_1]\times[\ell_2]\times[\ell_3]$ to \emph{local coordinates} $[n]\times[n]\times[n]$;

>>>>

\item extraction, from image arrays of the block views, depending on 3 Cartesian indices;

\item transform  each block \emph{from global} $[\ell_1]\times[\ell_2]\times[\ell_3]$ to \emph{local coordinates} $[n]\times[n]\times[n]$;
